Well-quasi-orderings on word languages

### 2025-09-05 src/introduction.tex
fix: sentences

\begin{figure}[h]
  \centering
  \begin{tabular}{c|c|c|c}
      \toprule
      $L$ & \textbf{Characterisation} & $\oWidth{L}$ & $\oType{L}$ \\
      \midrule
      arbitrary & \cref{infix-embedding:thm} & $< \omegaUncount$  & $< \omegaUncount$ \\
      bounded & \cref{bounded-language:thm} & $< \omegaOrd^2$ & $< \omegaOrd^3$ \\
      downwards closed & \cref{small-ordinal-invariants:thm} & $< \omegaOrd^2$ & $< \omegaOrd^3$ \\
      \bottomrule
    \end{tabular}
    \caption{Summary of results for the \kl{infix relation}.}
    \label{infixes-summary:fig}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{c|c|c|c}
      \toprule
      $L$ & \textbf{Characterisation} & $\oWidth{L}$ & $\oType{L}$ \\
      \midrule
      arbitrary & \cref{infix-embedding:thm} & $< \omegaOne$  & $< \omegaOne$ \\
      bounded & \cref{bounded-language:thm} & $< \omegaOrd^2$ & $< \omegaOrd^3$ \\
      downwards closed & \cref{small-ordinal-invariants:thm} & $< \omegaOrd^2$ & $< \omegaOrd^3$ \\
      \bottomrule
    \end{tabular}
    \caption{Summary of results for the \kl{infix relation}.}
    \label{infixes-summary:fig}
\end{figure}

### 2025-09-05 src/prelims.tex
fix: sentences

\AP
Let $(X, \leq)$ be a \kl{well-quasi-ordered} set. One can define three
well-founded trees from $X$: the tree of \kl{bad sequences}, the tree of
decreasing sequences, and the tree of \kl{antichains}. The rank of these
respective trees are called respectively the \intro{maximal order type} of $X$
written $\intro*{\oType{X}}$ \cite{dejongh77}, the \intro{ordinal height} of
$X$ written $\intro*{\oHeight{X}}$ \cite{schmidt81}, and the \intro{ordinal
width} of $X$ written $\intro*{\oWidth{X}}$ \cite{kriz90b}. These three
parameters are called the \intro{ordinal invariants} of a
\kl{well-quasi-ordered} set $X$. 
As an example, for $(\Nat, \leq)$, all bad sequences are descending and there are no antichains. Therefore the maximal order type and the ordinal height of $\Nat$ are $\omega$ and the ordinal width is 1. \todo{Please check this!}
We refer to the survey of \cite{DZSCSC20} for
a detail discussion on these concepts and their computation on specific classes
of well-quasi-ordered sets.

>>>>

\AP
Let $(X, \leq)$ be a \kl{well-quasi-ordered} set. One can define three
well-founded trees from $X$: the tree of \kl{bad sequences}, the tree of
decreasing sequences, and the tree of \kl{antichains}. The rank of these
respective trees are called respectively the \intro{maximal order type} of $X$
written $\intro*{\oType{X}}$ \cite{dejongh77}, the \intro{ordinal height} of
$X$ written $\intro*{\oHeight{X}}$ \cite{schmidt81}, and the \intro{ordinal
width} of $X$ written $\intro*{\oWidth{X}}$ \cite{kriz90b}. These three
parameters are called the \intro{ordinal invariants} of a
\kl{well-quasi-ordered} set $X$. We refer to the survey of \cite{DZSCSC20} for
a detail discussion on these concepts and their computation on specific classes
of well-quasi-ordered sets.
